\documentclass[12pt]{report}
\usepackage[thesis]{odusci}  
\usepackage{longtable}
\newcommand{\cc}[1]{}
\usepackage[backend=bibtex, style=science, sorting=nyt, maxnames=10, minnames=10]{biblatex}
\usepackage{setspace}

\addbibresource{ref.bib}
\setlength\intextsep{1.69cm}
\begin{document}
\title{Development of an Autonomous Cryogenics Plant Cool-Down}
\author{William Harris Buhrig IV}
\degrees{B.S. December 2023, Old Dominion University\\A.S. May 2022, Tidewater Community College}
\dept{Mechanical Engineering}
\submitdate{December 2025}
\principaladviser{K.N. Kaipa}
\coadviser{Brian Mastracci}
\member{Geoffrey Kraft}
\member{Jean Delayen}

%%%%% FRONT MATTER %%%%% 

%% Abstract - maximum 350 words
\abstract{This paper aims to outline the possible structure and application of a high-level planned control system to adjust and modify existing control structures implemented on all Thomas Jefferson National Laboratory (JLab) Cryogenic Refrigeration Plants to allow for future Autonomous cool-downs.}

%% Dedication - optional, 1 page max
\dedication{This dedication is for my Mom because you've been there through it all. Your support and understanding mean everything to me. We've definitely got the ticket now.}

%% Acknowledgements
\acknowledge{I want to start my list of acknowledgments with Dr. Geoffrey Kraft for giving me the opportunity in the first place to get where I am today by offering me a tour of the Old Dominion Center for Accelerator Physics and giving me the choice to join the Virginia Innovative Traineeships in Accelerators program.  Followed by both Dr. Krishnanand N. Kaipa and Brian Mastracci for always being there to support me in my goals.  I want to also acknowledge the entirety of the Cryogenics Department at Thomas Jefferson National Laboratory for being so supportive and providing so many affable conversations.\cc{If you want multiple paragraphs \\ \indent}}

%%%%% Nomenclature %%%%%
\input{Chapters/00_nomenclature}

%%%%% Before and After Acknowledgement Page %%%%%
\beforepreface
\afterpreface

%%%%% CHAPTERS %%%%% 
\input{Chapters/01_introduction}
\input{Chapters/02_literatureReview}
\input{Chapters/03_plantModel}
\input{Chapters/04_controlModel}
\input{Chapters/05_dataAcquisition}
\input{Chapters/06_dataAnalysis}
\input{Chapters/96_futureWork}
\input{Chapters/97_conclusion}
\cleardoublepage

%%%%% REFERENCES %%%%% 
\addtocontents{toc}{\vspace*{12pt}}
\nocite{*}
\printbibheading[heading=bibintoc, title={REFERENCES}]
\printbibliography[keyword={primary}, heading=none]
\printbibliography[keyword={supplemental}, heading=subbibintoc, title={SUPPLEMENTAL SOURCES CONSULTED}]

%%%%% APPENDICES %%%%% 
\input{Chapters/98_appendices}

%%%%% VITA - max 1 page %%%%% 
\input{Chapters/99_vita}
\end{document}